Strings functions analysis

### 2022-08-22 article.tex
Considered functions redo

    We should keep in mind that the number of string functions in different programming languages is very large, and this number can grow, as we said before, without limitations. For this reason, this article does not consider all existing functions, but only those that meet some criteria. \hl{<- Transfer to method}

@@

    In order to investigate functions, we have to make a list of functions to be investigated. For this purpose, programming languages such as Java, Python, C++, Ruby were chosen. They were chosen on the basis that they are quite popular, and they implement different paradigms (e.g. strict and non-strict typing in C++ and Python respectively).

    A table with the list of different functions from standard string libraries for these languages has been compiled. For the analysis will be selected functions, which are presented at least in two programming languages (out of four presented). Since for the functions presented only in one language, we can conclude that they are used in too special or rare cases.

>>>>

@@

    In order to investigate functions, we have to make a list of functions to be investigated. For this purpose, programming languages such as Java, Python, C++, Ruby, JavaScript, Go, C\#, Swift, PHP, Rust were chosen. They were chosen based on parameters such as the number of questions on StackOverflow, the number of repositories on GitHub with 100+ stars, and the TIOBE Index; and they implement different paradigms (e.g. strict and non-strict typing in C++ and Python respectively).

    We should keep in mind that the number of string functions in different programming languages is very large, and this number can grow, as we said before, without limitations. For this reason, this article does not consider all existing functions, but only those that meet some criteria.

    A table with the list of different functions from standard string libraries for these languages has been compiled. For the analysis will be selected functions, which are presented at least in three programming languages (out of ten presented). Since for the functions presented only in one-two language, we can conclude that they are used in too special or rare cases.
